---
title: "finalproj_re1032"

---

```{r setup, include=FALSE}
library(readxl)
library(ggplot2)
library(knitr)
library(gprofiler2)
genes <- read_excel("acylRACtotaldataset.xlsx")

```

Data analysis and Final Project for Data Science for Life Sciences (Fall2021).

The data analyzed here comes from an acyl-RAC experiment performed on Arabidopsis thaliana. Include explanation of what acyl-RAC is and palmitoylation.
```{r echo=FALSE}
#list number of proteins per cellular location
#new dataframe with unique subacon and number of genes associated with them
#way to remove number of rows?
df <- data.frame(matrix(ncol = 2, nrow = 0))
colnames(df) <- c('Subcellular Location', 'Gene Counts')
for (cell_location in unique(genes$SubaCon)){
  locations <- subset(genes, genes$SubaCon == cell_location) #subset dataframe of cellular location and genes in that location.
  gene_count <- nrow(locations)
  df[nrow(df) + 1,] = c(cell_location, gene_count)
  
}

kable(df)

```


```{r echo=FALSE}
#MapMin code 1. Range of codes 0-50


df2 <- data.frame(matrix(ncol = 2, nrow = 0))
colnames(df2) <- c('MapMan description', 'Gene counts')
for (code in unique(genes$`MapMan Bin1 Desc`)){
  process <- subset(genes, genes$`MapMan Bin1 Desc` == code) #subset dataframe of cellular location and genes in that location.
  gene_count <- nrow(process)
  df2[nrow(df2) + 1,] = c(code, gene_count)
  
}

kable(df2)

```
Important to note that this data from Arabidopsis, which is why we see things like 'Cell wall' and 'Phytohormones'. But also note that there's a significant number of genes that aren't assigned to any process. 


```{r echo=FALSE}



```




